Efficient High-Level Abstractions for Web Programming

### 2013-09-02 papers/gpce2013/gpce2013.tex
Explain the selector listing. Mention JavaScript libraries in the related works

Alternatively, one can define concepts relative to a specific domain as a library on top of a thin
general purpose language (it is also referred to as a domain-specific \emph{embedded}
language~\cite{Hudak96_DSEL}). Figure \ref{fig:langs} (c) depicts this approach. Defining such a
library requires minimal effort (though the syntax of the DSL is limited by the syntax flexibility
of the host language) and several DSLs can interoperate freely within the host language. However,
this approach gives no opportunity to efficiently translate a concept according to the target
platform characteristics because the compiler has no domain-specific knowledge (though some
compilers hard-code the translation of some common abstractions such as arrays to leverage the
target platform characteristics). Examples of languages following this approach are Java/GWT,
Kotlin, HaXe and SharpKit.

@@

Listing \ref{vanilla-selectors} gives an example of use of various functions from the native
selectors API to retrieve a list of input fields within a form. The existence of several
specialized functions in the API makes it possible to write efficient code, but forces users to
think at a low abstraction level.

@@

A high-level abstraction for searching elements in a document could be just one function
finding all elements matching a given CSS selector. In fact, most JavaScript
developers\footnote{According to
\href{http://trends.builtwith.com/javascript}{http://trends.builtwith.com/javascript}, jQuery is
used by more than 40\% of the top million sites.} use the jQuery library~\cite{Bibeault08_jQuery}
that actually provides only one function to search for elements. Listing \ref{jquery-selectors}
shows an equivalent JavaScript program as Listing \ref{vanilla-selectors}, but using jQuery. The
code is both shorter and simpler, thanks to its higher level of abstraction. jQuery provides an API
that is simpler to master because it has fewer functions, but this benefit comes at the price of a
decrease in runtime performance.

>>>>

Alternatively, one can define concepts relative to a specific domain as a library on top of a thin
general purpose language (it is also referred to as a domain-specific \emph{embedded}
language~\cite{Hudak96_DSEL}). Figure \ref{fig:langs} (c) depicts this approach. Defining such a
library requires minimal effort (though the syntax of the DSL is limited by the syntax flexibility
of the host language) and several DSLs can interoperate freely within the host language. However,
this approach gives no opportunity to efficiently translate a concept according to the target
platform characteristics because the compiler has no domain-specific knowledge (though some
compilers hard-code the translation of some common abstractions such as arrays to leverage the
target platform characteristics). Examples of languages following this approach are Java/GWT,
Kotlin, HaXe and SharpKit. Libraries written in JavaScript (\eg{} jQuery~\cite{Bibeault08_jQuery}) also match this category though most of them do not support both client and server sides.

@@

Listing \ref{vanilla-selectors} gives an example of use of various functions from the native
selectors API to retrieve a list of input fields within a form. The \code{getWords} function first finds in the document the HTML element with id \code{add-user}, then collects all its \code{fieldset} children elements, and for each one returns the list of its children elements having class \code{word}. The existence of several specialized functions in the API makes it possible to write efficient code, but forces users to think at a low abstraction level.

@@

A high-level abstraction for searching elements in a document could be just one function
finding all elements matching a given CSS selector. In fact, most JavaScript
developers\footnote{According to
\href{http://trends.builtwith.com/javascript}{http://trends.builtwith.com/javascript}, jQuery is
used by more than 40\% of the top million sites.} use the jQuery library
that actually provides only one function to search for elements. Listing \ref{jquery-selectors}
shows an equivalent JavaScript program as Listing \ref{vanilla-selectors}, but using jQuery. The
code is both shorter and simpler, thanks to its higher level of abstraction. jQuery provides an API
that is simpler to master because it has fewer functions, but this benefit comes at the price of a
decrease in runtime performance.
